---
title: "Final Project First Plot"
author: "Zulin Zhou (zz69), Zhanhang Zhou (zz70) "
output:
  pdf_document:
    fig_height: 5
    fig_width: 5
  html_document:
    df_print: paged
date: 'Thursday October 22, 3:30pm'
---

#### Introduction
We want to track pollutants levels in the air over US, especially in Texas, and observe if they are effected by other weather conditions. The main pollutant in the air is O3(ozone), so we will be tracking on that. Other pollutants level might have differnet importance in different districts so we are also planning to research on those factors

#### Datasets
We are using data from the official EPA website https://www.epa.gov/castnet. The main table is 22,290,625X17. The table takes weather conditions and ozone rates into consideration by scale of hour. We also have side charts indicating similar data by day, week and season. And there's side charts that set down other pollutants including SO2, HNO3, ammonium and so on weekly scale.

The main table includes the following factors:
1. SITE_ID, which stands for Site identification code, in form of CHAR
2. DATE_TIME, in form of STRING
3. WIND_DIRECTION, in form of NUMBER
4. WINDSPEED_SCALAR, which stands for scalar wind speed, in form of NUMBER
5. OZONE, in form of NUMBER
6. SOLAR_RADIATION, in form of NUMBER
7. FLOW_RATE, in form of NUMBER
8. SHELTER_TEMPERATURE, in form of NUMBER
9. QA_CODE, which stand for Quality assurance level of the record, in form of CHAR
10. SIGMA_THETA, which stands for Standard deviation of wind direction, in form of NUMBER
11. WETNESS, in form of NUMBER
12. TEMPERATURE, in form of NUMBER
13. UPDATE_DATE, in form of STRING
14. WINDSPEED, which stands for vector wind speed, in form of NUMBER
15. TEMPERATURE_DELTA, which stands for Temperature difference between 9m and 2m probes, in form of NUMBER
16. PRECIPITATION, in form of NUMBER
17. RELATIVE_HUMIDITY, in form of NUMBER

#### First Plot
Showing the percipitation (reflected by flow rate), ozone level and temperature for Texas in Year 2015-2019. Data subsetted through webpage API.

First load the subsetted data
```{r, echo=TRUE}
library(ggplot2)
library(readr)
Meteorological_Hourly <- read_csv("Meteorological - Hourly.csv")
```

Strip date and related variables
```{r, echo=TRUE}
setTime <- strptime(Meteorological_Hourly$DATE_TIME, "%m/%d/%Y %H:%M:%S")
```

```{r, echo=TRUE, fig.align='center', fig.height=9, fig.width=11}
year <- as.numeric(format(setTime,'%Y'))
date <- as.numeric(format(setTime,'%d'))
temperature <- Meteorological_Hourly$TEMPERATURE
ozone <- Meteorological_Hourly$OZONE
rainfall <- Meteorological_Hourly$FLOW_RATE
plotData <- data.frame(rainfall,ozone,temperature,year,date)
```

Plot and facet_wrap by year
```{r, echo=TRUE, fig.align='center', fig.height=9, fig.width=11}
ggplot(plotData) + 
  geom_line(aes(x = date, y = ozone), color = "blue") +
  geom_line(aes(x = date, y = rainfall), color = "red") +
  geom_line(aes(x = date, y = temperature), color = "green") +
  facet_wrap(~year,ncol = 3) +
  labs(title = "Fluctuation of ozone, rainfall and temperature by Year",
       x = "Date",
       y = "Value")
```
